---
name: Rizqy Amelia
surname: Zein
position: "Assitant Professor"
address: "Department of Personality and Social Psychology, Universitas Airlangga"
phone: +62 811 253 0 777
www: rameliaz.github.io
email: amelia.zein@psikologi.unair.ac.id
twitter: ameliazein
github: rameliaz
date: "`r format(Sys.time(), '%B %Y')`"
qualifications: S.Psi., M.Sc.
aboutme: Social Psychology, Science Communication, Research Methods, R, Statistics
profilepic: foto.jpeg
headcolor: 414141
output: 
  vitae::moderncv:
  theme: banking
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyverse)
library(lubridate)
library(here)
library(readxl)
library(glue)
library(scholar)
```

```{r edu, include=FALSE}
edu.raw <- read_csv(here::here("data", "education.csv"))
edu <-
  edu.raw %>% 
  fill(degree, start, end, uni, location, details) %>%  
  mutate(start = dmy(start),
         end = dmy(end)) %>% 
  mutate(when = case_when(
    year(start) == year(end) ~ year(end) %>% as.character(),
    TRUE ~ glue("{year(start)}--{year(end)}") %>% as.character()
  ))
```

```{r experience, include=FALSE}
jobs.raw <- read_csv(here::here("data", "jobs.csv"))
jobs <-
  jobs.raw %>% 
  fill(start, end, what, with, where, tag) %>%  
  mutate(start = dmy(start),
         end = dmy(end)) %>% 
  mutate(when = case_when(
    is.na(end) ~ glue("{year(start)}--Present") %>% as.character(),
    year(start) == year(end) ~ year(end) %>% as.character(),
    TRUE ~ glue("{year(start)}--{year(end)}") %>% as.character()
  ))
```

```{r presentations, include=FALSE}
presentations.raw <- read_csv(here("data", "presentation.csv"))
presentations <- 
  presentations.raw %>% 
  mutate(when = dmy(when)) %>% 
  arrange(desc(when))
```

```{r prof-devel, include=FALSE}
development.raw <- read_csv(here("data", "personal development.csv"))
development <- 
  development.raw %>% 
  mutate(when = dmy(when)) %>% 
  arrange(desc(when))
```

```{r awards, include=FALSE}
awards.raw <- read_csv(here("data", "awards & grants.csv"))
awards <- awards.raw %>% 
  mutate(when = dmy(when)) %>% 
  arrange(desc(when))
```


```{r pubs, include=FALSE}
pubs.raw <- read_csv(here("data", "publications.csv"))
pubs <- pubs.raw %>% 
  mutate(when = dmy(when)) %>% 
  arrange(desc(when))
```


# Introduction
As an aspiring PhD, I’m interested in conducting research on **science denialism** by looking at its relation with **conspiracy belief**, **collective narcissism**, **epistemic virtue/belief**, **religiosity** and **general/intellectual humility**. I’m also very passionate about **research methods**, **meta-research**, **reproducibility**, **psychometrics**, and **advanced statistical analysis**.

# Education 

```{r education}
edu %>% 
  arrange(desc(start)) %>% 
  detailed_entries(
    what = degree,
    when = when,
    with = uni,
    where = location,
    why = details
  )

```


# Research Experience

```{r research}

jobs %>% 
  filter(tag == "research") %>% 
  arrange(desc(start)) %>%
  detailed_entries(
    what = what,
    when = when,
    with = with,
    why = why,
    where = where
  )
```


# Teaching Experience

```{r teaching}

jobs %>% 
  filter(tag=="teaching") %>% 
  arrange(desc(start)) %>% 
  detailed_entries(
    what = what,
    when = when,
    with = with,
    why = why,
    where = where
  )
```

# Awards & Grants

```{r aw}
awards %>% 
  arrange(desc(when)) %>%
  detailed_entries(
    what = what,
    when = when,
    with = with,
    why = why,
    where = where
  )
```


# Publications

## Op-Ed Articles in Mass Media

```{r op}
pubs %>% 
  filter(tag == "op") %>% 
  arrange(desc(when)) %>%
  detailed_entries(
    what = what,
    when = when,
    with = with,
    why = why,
    where = where
  )
```

## Peer-Reviewed Articles

```{r pub}
pubs %>% 
  filter(tag == "peer") %>% 
  arrange(desc(when)) %>% 
  detailed_entries(
    what = what,
    when = when,
    with = with,
    why = why,
    where = where
  )
```


# Community Service

## Manuscript Reviewer
 * Journal of Ethnic and Migration Studies (2)
 * PLoS One (6)
 * Psychology and Sexuality (1)
 * Psychology Research and Behavior Management (1)
 
## Other

```{r}
jobs %>%
  filter(tag == "service") %>% 
  arrange(desc(when)) %>% 
  detailed_entries(
    what = what,
    when = when,
    with = with,
    where = where,
    why = why
  )
```


# Presentation

## Conference Presentation

```{r}
presentations %>%
  filter(tag == "conference") %>% 
  arrange(desc(when)) %>% 
  detailed_entries(
    what = what,
    when = when,
    with = with,
    where = where,
    why = why
  )
```


## Poster Presentation

```{r}
presentations %>%
  filter(tag == "poster") %>% 
  arrange(desc(when)) %>% 
  detailed_entries(
    what = what,
    when = when,
    with = with,
    where = where,
    why = why
  )
```


## Invited Talk

```{r}
presentations %>%
  filter(tag == "invited talk") %>% 
  arrange(desc(when)) %>% 
  detailed_entries(
    what = what,
    when = when,
    with = with,
    where = where,
    why = why
  )
```


## Workshop

```{r}
presentations %>%
  filter(tag == "workshop") %>% 
  arrange(desc(when)) %>% 
  detailed_entries(
    what = what,
    when = when,
    with = with,
    where = where,
    why = why
  )
```


## Live TV Talkshow

```{r}
presentations %>%
  filter(tag == "live talkshow") %>% 
  arrange(desc(when)) %>% 
  detailed_entries(
    what = what,
    when = when,
    with = with,
    where = where,
    why = why
  )
```



# Professional Development

## Workshop

```{r}
development %>%
  filter(why == "workshop") %>% 
  arrange(desc(when)) %>% 
  brief_entries(
    what = what,
    when = when,
    with = with
  )
```

## MOOC

```{r}
development %>%
  filter(why == "mooc") %>% 
  arrange(desc(when)) %>% 
  brief_entries(
    what = what,
    when = when,
    with = with
  )
```

## Summer School

```{r}
development %>%
  filter(why == "summer school") %>% 
  arrange(desc(when)) %>% 
  brief_entries(
    what = what,
    when = when,
    with = with
  )
```

## Professional Membership

```{r}
jobs %>%
  filter(tag == "profesional") %>% 
  arrange(desc(when)) %>% 
  brief_entries(
    what = with,
    when = when,
    with = where
  )
```

# Part-time Jobs

```{r}
jobs %>%
  filter(tag == "other") %>% 
  arrange(desc(when)) %>% 
  detailed_entries(
    what = what,
    when = when,
    with = with,
    where = where,
    why = why
  )
```


# Skills
  * Academic writing
  * Advanced statistical analysis
    - Multi-level modeling, latent variable modeling (structural equation modeling, mixture models), general linear modeling, generalised linear models
  * Advanced psychometrics analysis
    - Latent response model
  * Research methods
    - Cross-sectional survey, experiments, systematic review, & meta-analysis
  * R programming
    - `lavaan`, `psych`, `lme4`, `papaja`, `xaringan`, `blogdown`, `bookdown`, `metaverse`, & `tidyverse`


# Other Activities
  * Cooking
  * Cycling
  * Reading science fiction
  * Watching food/culinary documentary on Netflix